\textbf{ CMCS 818J Project Milestone Report } \\ \small{Christopher Imbriano \& Behzad Koosha}

### 2012-11-04 doc/milestone_draft1.tex
One sentence per line

%In the following, we will represent the steps that the streaming authenticated data structure follows to implement range search queries.
Taking into account that the bottomline of our scheme is the Merkle tree structure and using lattice based hash
function with homomorphic property, we are implementing the algorithm in Python or Ruby language at this stage and 
actually testing and configuring different steps in the algorithm i.e. \texttt{genkey, initialize, updateVerifier, updateProver, query, verify}.   \\

Languages such as Python or Ruby have support for their community of users that grows up and that
is one of its most important strengths. Ruby has a vibrant and growing community that is friendly towards
people of all skill levels. Such groups allow users to network with other Ruby
programmers.  \\

As for Python, NumPy is an extension module which provides efficient operations on arrays of data allowing
Python to operate as a high level language for manipulating numerical data.
In addition, SciPy is a set of open source scientific and numerical tools for Python. It can 
support special functions, integration, differential equation solvers, etc. \\

We are also thinking to use some software system such as EventMachine that is designed for writing
scalable applications in Ruby. EventMachine has been used for making various libraries and frameworks
in which concurrency is considered. Examples of such application could be
web servers and proxies, email and IM, authentication and authorization processors and 
network applications. \\

In our work, we have generated a secret and public key depending on the size of the stream and the 
security parameter. The next step was to generate the hash function according to each left and right leaf. 
The hash function is computed as $ h(x,y) = Lx + Ry $ where \textbf{L, R} are selected randomly from $Z_{q}^{k \times m}$ and
\textbf{x,y} are vectors of small norm. \\

@@

\section{Implementation Issues\\}
\subsection{Proof of Concept}
\begin{enumerate}
\item In order to implement a streaming authenticated data structure based on lattices, a fast
arithmetic library for matrices and vector is required.
\item Matrix multiplication mod \texttt{q} ( \texttt{q poly(k)}) is needed.
\end{enumerate}

\subsection{Applicable Libraries\\}
\begin{enumerate}
\item \textbf{NTL 5.5.2} : A free software written in C++ providing data structures and algorithms for arbitrary length
integers, for vectors, matrices and polynomials over the integers and over the finite fields and for 
arbitrary precision floating point arithmetic. \texttt{http://shoup.net/ntl/}
\item \textbf{MAGMA V2.18} : The kernel of Magma contains implementations of many of
the important concrete classes of 
structure in five fundamental branches of algebra, namely group theory, ring theory, field theory, 
module theory and the theory of algebras. In addition, certain
families of structures from algebraic 
geometry and finite incidence geometry are included. \texttt{http://magma.maths.usyd.edu.au/}
\end{enumerate}

\subsection{ Library Prototype\\}

>>>>

%In the following, we will represent the steps that the streaming authenticated data structure follows to implement range search queries.
Taking into account that the bottomline of our scheme is the Merkle tree structure and using lattice based hash function with homomorphic property, we are implementing the algorithm in ython or Ruby language at this stage and actually testing and configuring different steps in the algorithm i.e. \texttt{genkey, initialize, updateVerifier, updateProver, query, verify}.

Languages such as Python or Ruby have support for their community of users that grows up and that
is one of its most important strengths.
Ruby has a vibrant and growing community that is friendly towards people of all skill levels.
Such groups allow users to network with other Ruby programmers.

As for Python, NumPy is an extension module which provides efficient operations on arrays of data allowing Python to operate as a high level language for manipulating numerical data.
In addition, SciPy is a set of open source scientific and numerical tools for Python.
It can support special functions, integration, differential equation solvers, etc.

We are also thinking to use some software system such as EventMachine that is designed for writing
scalable applications in Ruby.
EventMachine has been used for making various libraries and frameworks in which concurrency is considered.
Examples of such application could be web servers and proxies, email and IM, authentication and authorization processors and network applications.

In our work, we have generated a secret and public key depending on the size of the stream and the security parameter.
The next step was to generate the hash function according to each left and right leaf.
The hash function is computed as $ h(x,y) = Lx + Ry $ where \textbf{L, R} are selected randomly from $Z_{q}^{k \times m}$ and
\textbf{x,y} are vectors of small norm.

@@

\section{Implementation Issues}
\subsection{Proof of Concept}
\begin{enumerate}
\item In order to implement a streaming authenticated data structure based on lattices, a fast
arithmetic library for matrices and vector is required.
\item Matrix multiplication mod \texttt{q} ( \texttt{q poly(k)}) is needed.
\end{enumerate}

\subsection{Applicable Libraries}
\begin{enumerate}
\item \textbf{NTL 5.5.2} : A free software written in C++ providing data structures and algorithms for arbitrary length
integers, for vectors, matrices and polynomials over the integers and over the finite fields and for
arbitrary precision floating point arithmetic. \texttt{http://shoup.net/ntl/}
\item \textbf{MAGMA V2.18} : The kernel of Magma contains implementations of many of the important concrete classes of structure in five fundamental branches of algebra, namely group theory, ring theory, field theory, module theory and the theory of algebras.
In addition, certain families of structures from algebraic geometry and finite incidence geometry are included. \texttt{http://magma.maths.usyd.edu.au/}
\end{enumerate}

\subsection{ Library Prototype}
